\thetitle

### 2021-04-30 writing/discussion.tex
In Transient threats, clarify when we talk about Python benchmarks

At first glance, these measurements seem to contradict the results
of~\citet{vss-popl-2017}. They report an average slowdown of 2.5x and a
worst-case of 5.4x on fully-typed benchmarks in Reticulated Python.
Unfortunately, the high cost of Shallow Racket seems closer to the truth.
There are at least four broad issues that skew the earlier results:
\begin{enumerate}

@@

\item On non-trivial programs, Reticulated Python suffers from the same high
overhead as Shallow Racket.  It runs the simplest benchmark from the suite 
in approximately 40 seconds without blame and times out after 10 minutes when
the blame map is enabled.

>>>>

At first glance, these measurements seem to contradict the results
of~\citet{vss-popl-2017}. They report an average slowdown of 2.5x and a
worst-case of 5.4x on the fully-typed Python benchmarks in Reticulated Python.
Unfortunately, the high cost of Shallow Racket seems closer to the truth.
There are at least four broad issues that skew the earlier results:
\begin{enumerate}

@@

\item On non-trivial programs, Reticulated Python suffers from the same high
overhead as Shallow Racket.  It runs the simplest benchmark from the GTP suite (translated into Python)
in approximately 40 seconds without blame and times out after 10 minutes when
the blame map is enabled.
